### 2025-05-20 SuppSections.Rmd
Updated data by season by year section.

acs1 <- AC_stos %>% filter(length > 17 & length <= 45)
acs2 <- AC_stos %>% filter(length > 45)
aps1 <- AP_stos %>% filter(length > 29)
ghs1 <- GH_stos %>% filter(length > 19 & length <= 40)
ghs2 <- GH_stos %>% filter(length > 40)

acs0 <- AC_stos %>% filter(length < 18)
aps0 <- AP_stos %>% filter(length < 30)
ghs0 <- GH_stos %>% filter(length < 20)

# table(acs0$pa, acs0$year)
# table(acs1$pa, acs1$year)
# table(acs2$pa, acs2$year)
# table(aps0$pa, aps0$year)
# table(aps1$pa, aps1$year)
# table(ghs0$pa, ghs0$year)
# table(ghs1$pa, ghs1$year)
# table(ghs2$pa, ghs2$year)

Eacs1 <- AC_stos %>% filter(length > 17 & length <= 45) %>% filter(year != 1995)
Eacs2 <- AC_stos %>% filter(length > 45) %>% filter(year != 1995)
Eaps1 <- AP_stos %>% filter(length > 29)
Eghs1 <- GH_stos %>% filter(length > 19 & length <= 40)
Eghs2 <- GH_stos %>% filter(length > 40)

Eacs0 <- AC_stos %>% filter(length < 18) %>% filter(year == 1982)
Eaps0 <- AP_stos %>% filter(length < 30) %>% filter(year != 1984)
Eghs0 <- GH_stos %>% filter(length < 20) %>% filter(year != 1984)

@@

acf1 <- AC_stof %>% filter(length > 17 & length <= 45)
acf2 <- AC_stof %>% filter(length > 45)
apf1 <- AP_stof %>% filter(length > 29)
ghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
ghf2 <- GH_stof %>% filter(length > 40)

acf0 <- AC_stof %>% filter(length < 18)
apf0 <- AP_stof %>% filter(length < 30)
ghf0 <- GH_stof %>% filter(length < 20)

# table(acf0$pa, acf0$year)
# table(acf1$pa, acf1$year)
# table(acf2$pa, acf2$year)
# table(apf0$pa, apf0$year)
# table(apf1$pa, apf1$year)
# table(ghf0$pa, ghf0$year)
# table(ghf1$pa, ghf1$year)
# table(ghf2$pa, ghf2$year)

Eacf1 <- AC_stof %>% filter(length > 17 & length <= 45)
Eacf2 <- AC_stof %>% filter(length > 45) %>% filter(year != 1994)
Eapf1 <- AP_stof %>% filter(length > 29)
Eghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
Eghf2 <- GH_stof %>% filter(length > 40)

Eacf0 <- AC_stof %>% filter(length < 18) %>% filter(year == 1982 & year == 1983 & year == 1988)
Eapf0 <- AP_stof %>% filter(length < 30)
Eghf0 <- GH_stof %>% filter(length < 20)

@@

### Total
```{r}
Eac0 <- rbind(acs0, acf0) %>% mutate(alt.name = "Atlantic cod")
Eac1 <- rbind(acs1, acf1) %>% mutate(alt.name = "Atlantic cod")
Eac2 <- rbind(acs2, acf2) %>% mutate(alt.name = "Atlantic cod")
Eap0 <- rbind(aps0, apf0) %>% mutate(alt.name = "American plaice")
Eap1 <- rbind(aps1, apf1) %>% mutate(alt.name = "American plaice")
Egh0 <- rbind(ghs0, ghf0) %>% mutate(alt.name = "Greenland halibut")
Egh1 <- rbind(ghs1, ghf1) %>% mutate(alt.name = "Greenland halibut")
Egh2 <- rbind(ghs2, ghf2) %>% mutate(alt.name = "Greenland halibut")

@@

acs1 <- AC_stos %>% filter(length > 17 & length <= 45)
acs2 <- AC_stos %>% filter(length > 45)
aps1 <- AP_stos %>% filter(length > 29)
ghs1 <- GH_stos %>% filter(length > 19 & length <= 40)
ghs2 <- GH_stos %>% filter(length > 40)

acs0 <- AC_stos %>% filter(length < 18)
aps0 <- AP_stos %>% filter(length < 30)
ghs0 <- GH_stos %>% filter(length < 20)

# table(acs0$pa, acs0$year)
# table(acs1$pa, acs1$year)
# table(acs2$pa, acs2$year)
# table(aps0$pa, aps0$year)
# table(aps1$pa, aps1$year)
# table(ghs0$pa, ghs0$year)
# table(ghs1$pa, ghs1$year)
# table(ghs2$pa, ghs2$year)

Cacs1 <- AC_stos %>% filter(length > 17 & length <= 45) %>% filter(year != 1998 & year != 2017)
Cacs2 <- AC_stos %>% filter(length > 45) %>% filter(year != 2015)
Caps1 <- AP_stos %>% filter(length > 29) %>% filter(year != 2017)
Cghs1 <- GH_stos %>% filter(length > 19 & length <= 40) %>% filter(year != 2017)
Cghs2 <- GH_stos %>% filter(length > 40)

Cacs0 <- AC_stos %>% filter(length < 18) %>% filter(year != 1996 & year != 1998 & year != 1999 & year != 2006 & year != 2011 & year != 2017)
Caps0 <- AP_stos %>% filter(length < 30) %>% filter(year != 2017)
Cghs0 <- GH_stos %>% filter(length < 20) %>% filter(year != 2015 & year != 2017)

@@

acf1 <- AC_stof %>% filter(length > 17 & length <= 45)
acf2 <- AC_stof %>% filter(length > 45)
apf1 <- AP_stof %>% filter(length > 29)
ghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
ghf2 <- GH_stof %>% filter(length > 40)

acf0 <- AC_stof %>% filter(length < 18)
apf0 <- AP_stof %>% filter(length < 30)
ghf0 <- GH_stof %>% filter(length < 20)

# table(acf0$pa, acf0$year)
# table(acf1$pa, acf1$year)
# table(acf2$pa, acf2$year)
# table(apf0$pa, apf0$year)
# table(apf1$pa, apf1$year)
# table(ghf0$pa, ghf0$year)
# table(ghf1$pa, ghf1$year)
# table(ghf2$pa, ghf2$year)

Cacf1 <- AC_stof %>% filter(length > 17 & length <= 45)
Cacf2 <- AC_stof %>% filter(length > 45) %>% filter(year != 1995)
Capf1 <- AP_stof %>% filter(length > 29) %>% filter(year != 2014)
Cghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
Cghf2 <- GH_stof %>% filter(length > 40)

Cacf0 <- AC_stof %>% filter(length < 18) %>% filter(year != 2011 & year != 2020)
Capf0 <- AP_stof %>% filter(length < 30) %>% filter(year != 2014)
Cghf0 <- GH_stof %>% filter(length < 20)

@@

ac <- data.frame(year = seq(1984,2020,1), 
                 ac0_spring = c(rep(0,11), dfac0$ac0_spring[1:16], 0, dfac0$ac0_spring[17:24], rep(0,1)),
                 ac1_spring = c(dfac1$ac1_spring),
                 ac2_spring = c(dfac2$ac2_spring[1:11], 0, dfac2$ac2_spring[12:36]),

                 ac0_fall = c(rep(0,11), dfac0$ac0_fall[1:16], 0, dfac0$ac0_fall[17:24], rep(0,1)),
                 ac1_fall = c(dfac1$ac1_fall),
                 ac2_fall = c(dfac2$ac2_fall[1:11], 0, dfac2$ac2_fall[12:36]))
write.csv(ac, file = "./Extra/acseason.csv")

@@

## - Table 1
```{r}

sample_size <- data.frame(
  E.C.Spr = c(nrow(filter(Tac0, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tac1, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tac2, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tgh0, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tgh1, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tgh2, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tap0, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tap1, geartype == "engel" & season == "spring" & content == "called"))),
  E.C.Fall = c(nrow(filter(Tac0, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tac1, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tac2, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tgh0, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tgh1, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tgh2, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tap0, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tap1, geartype == "engel" & season == "fall" & content == "called"))),
  E.F.Spr = c(nrow(filter(Tac0, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tac1, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tac2, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tgh0, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tgh1, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tgh2, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tap0, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tap1, geartype == "engel" & season == "spring" & content == "full"))),
  E.F.Fall = c(nrow(filter(Tac0, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tac1, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tac2, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tgh0, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tgh1, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tgh2, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tap0, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tap1, geartype == "engel" & season == "fall" & content == "full"))),
  E.pempty =  c(nrow(filter(Tac0, geartype == "engel" & pa == "0"))/nrow(filter(Tac0, geartype == "engel"))*100,
                nrow(filter(Tac1, geartype == "engel" & pa == "0"))/nrow(filter(Tac1, geartype == "engel"))*100,
                nrow(filter(Tac2, geartype == "engel" & pa == "0"))/nrow(filter(Tac2, geartype == "engel"))*100,
                nrow(filter(Tgh0, geartype == "engel" & pa == "0"))/nrow(filter(Tgh0, geartype == "engel"))*100,
                nrow(filter(Tgh1, geartype == "engel" & pa == "0"))/nrow(filter(Tgh1, geartype == "engel"))*100,
                nrow(filter(Tgh2, geartype == "engel" & pa == "0"))/nrow(filter(Tgh2, geartype == "engel"))*100,
                nrow(filter(Tap0, geartype == "engel" & pa == "0"))/nrow(filter(Tap0, geartype == "engel"))*100,
                nrow(filter(Tap1, geartype == "engel" & pa == "0"))/nrow(filter(Tap1, geartype == "engel"))*100),

  C.C.Spr = c(nrow(filter(Tac0, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tac1, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tac2, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tgh0, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tgh1, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tgh2, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tap0, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tap1, geartype == "campelen" & season == "spring" & content == "called"))),
  C.C.Fall = c(nrow(filter(Tac0, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tac1, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tac2, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tgh0, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tgh1, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tgh2, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tap0, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tap1, geartype == "campelen" & season == "fall" & content == "called"))),
  C.F.Spr = c(nrow(filter(Tac0, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tac1, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tac2, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tgh0, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tgh1, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tgh2, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tap0, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tap1, geartype == "campelen" & season == "spring" & content == "full"))),
  C.F.Fall = c(nrow(filter(Tac0, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tac1, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tac2, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tgh0, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tgh1, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tgh2, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tap0, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tap1, geartype == "campelen" & season == "fall" & content == "full"))),
  C.pempty =  c(nrow(filter(Tac0, geartype == "campelen" & pa == "0"))/nrow(filter(Tac0, geartype == "campelen"))*100,
                nrow(filter(Tac1, geartype == "campelen" & pa == "0"))/nrow(filter(Tac1, geartype == "campelen"))*100,
                nrow(filter(Tac2, geartype == "campelen" & pa == "0"))/nrow(filter(Tac2, geartype == "campelen"))*100,
                nrow(filter(Tgh0, geartype == "campelen" & pa == "0"))/nrow(filter(Tgh0, geartype == "campelen"))*100,
                nrow(filter(Tgh1, geartype == "campelen" & pa == "0"))/nrow(filter(Tgh1, geartype == "campelen"))*100,
                nrow(filter(Tgh2, geartype == "campelen" & pa == "0"))/nrow(filter(Tgh2, geartype == "campelen"))*100,
                nrow(filter(Tap0, geartype == "campelen" & pa == "0"))/nrow(filter(Tap0, geartype == "campelen"))*100,
                nrow(filter(Tap1, geartype == "campelen" & pa == "0"))/nrow(filter(Tap1, geartype == "campelen"))*100)

sample_size <- sample_size %>% mutate(E.pempty = format(E.pempty, digits = 4), C.pempty = format(C.pempty, digits = 4))

write.csv(x = sample_size, file = "./Extra/samplesize.csv")

@@

  geom_line( aes(x = time, y = ac1, colour = "ac", linetype = "medium"), size = 1.4) +
  geom_line(aes(x = time, y = ac2, colour = "ac", linetype = "large"), size = 1.4) +

  geom_line(aes(x = time, y = gh1, colour = "gh", linetype = "medium"), size = 1.4) +
  geom_line(aes(x = time, y = gh2, colour = "gh", linetype = "large"), size = 1.4) +

  geom_line(aes(x = time, y = ap1, colour = "ap", linetype = "medium"), size = 1.4) +

  scale_x_continuous(name = "Year", expand = c(0.009,0), limits = c(1983.9,1995.2), breaks = c(seq(1983,1995, 2))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.0,1.7)) +
  scale_color_manual(name = "", values = c(trawl = "brown", ac = "#BC8DA0", gh = "#048BA8", ap = "#AFD5AA"),
                     labels = c(trawl = "Trawl", ac = "Atlantic cod", gh = "Greenland halibut", ap = "American plaice")) +
  scale_linetype_manual(name = "", values = c(medium = "solid", large = "dotdash"),
                        labels = c(medium = "Medium", large = "Large")) +
  ggtitle("Engel\na) 3L Spring") +
  theme_classic() +
  theme(legend.position = "none", 
        axis.title.x = element_blank(),
        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))

@@

  geom_line( aes(x = time, y = ac1, colour = "ac", linetype = "medium"), size = 1.4) +
  geom_line(aes(x = time, y = ac2, colour = "ac", linetype = "large"), size = 1.4) +

  geom_line(aes(x = time, y = gh1, colour = "gh", linetype = "medium"), size = 1.4) +
  geom_line(aes(x = time, y = gh2, colour = "gh", linetype = "large"), size = 1.4) +

  geom_line(aes(x = time, y = ap1, colour = "ap", linetype = "medium"), size = 1.4) +

  scale_x_continuous(name = "Year", expand = c(0.009,0), limits = c(1983.9,1995.2), breaks = c(seq(1983,1995, 2))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0)) +
  scale_color_manual(name = "", values = c(trawl = "brown", ac = "#BC8DA0", gh = "#048BA8", ap = "#AFD5AA"),
                     labels = c(trawl = "Trawl", ac = "Atlantic cod", gh = "Greenland halibut", ap = "American plaice")) +
  scale_linetype_manual(name = "", values = c(medium = "solid", large = "dotdash"),
                        labels = c(medium = "Medium", large = "Large")) +
  ggtitle("c) 2J3KL Fall") + 
  theme_classic() +
  theme(legend.position = "none",
        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))

@@

# plot
sc <- ggplot(data = plotdf) +  
  geom_line(aes(x = time, y = ts, colour = "trawl"), size = 1.4, linetype = "dashed") +

  geom_line( aes(x = time, y = ac1, colour = "ac"), size = 1.4, linetype = "solid") +

  geom_line(aes(x = time, y = gh1, colour = "gh"), size = 1.4, linetype = "solid") +

  geom_line(aes(x = time, y = ap1, colour = "ap"), size = 1.4, linetype = "solid") +

@@

  geom_line( aes(x = time, y = ac1, colour = "ac", linetype = "medium"), size = 1.4) +
  geom_line(aes(x = time, y = ac2, colour = "ac", linetype = "large"), size = 1.4) +

  geom_line(aes(x = time, y = gh1, colour = "gh", linetype = "medium"), size = 1.4) +
  geom_line(aes(x = time, y = gh2, colour = "gh", linetype = "large"), size = 1.4) +

  geom_line(aes(x = time, y = ap1, colour = "ap", linetype = "medium"), size = 1.4) +

  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1994.9,2022), breaks = c(seq(1995, 2022, 5))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.32, 1.6)) +
  scale_color_manual(name = "", values = c(trawl = "brown", ac = "#BC8DA0", gh = "#048BA8", ap = "#AFD5AA"),
                     labels = c(trawl = "Trawl", ac = "Atlantic cod", gh = "Greenland halibut", ap = "American plaice")) +
  scale_linetype_manual(name = "", values = c(medium = "solid", large = "dotdash"),
                        labels = c(medium = "Medium", large = "Large")) +
  ggtitle("d) 2J3KL Fall") + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title.y = element_blank(),
        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))

```
## - Figure 2
```{r, fig.height=10, fig.width=12}

p1 <- ggarrange(se,
          sc,
          fe,
          fc,
          nrow = 2, ncol = 2,
          align = "v", common.legend = TRUE,
          legend = "right", legend.grob = ggpubr::get_legend(fc+theme(legend.position = "right", lengend.text = element_text(size = 15))))

ggsave(filename = "inputdata1.tiff", device = "tiff", plot = p1, path = "./Figures",
       dpi = 300, width = 14, height = 10, units = "in")

>>>>

Eacs1 <- AC_stos %>% filter(length > 17 & length <= 45)
Eacs2 <- AC_stos %>% filter(length > 45)
Eghs1 <- GH_stos %>% filter(length > 19 & length <= 40)
Eghs2 <- GH_stos %>% filter(length > 40)
Eaps1 <- AP_stos %>% filter(length > 29)

Eacs0 <- AC_stos %>% filter(length < 18)
Eghs0 <- GH_stos %>% filter(length < 20)
Eaps0 <- AP_stos %>% filter(length < 30)

# table(Eacs0$pa, Eacs0$year)
# table(Eacs1$pa, Eacs1$year)
# table(Eacs2$pa, Eacs2$year)
# table(Eghs0$pa, Eghs0$year)
# table(Eghs1$pa, Eghs1$year)
# table(Eghs2$pa, Eghs2$year)
# table(Eaps0$pa, Eaps0$year)
# table(Eaps1$pa, Eaps1$year)

@@

Eacf1 <- AC_stof %>% filter(length > 17 & length <= 45)
Eacf2 <- AC_stof %>% filter(length > 45)
Eghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
Eghf2 <- GH_stof %>% filter(length > 40)
Eapf1 <- AP_stof %>% filter(length > 29)

Eacf0 <- AC_stof %>% filter(length < 18)
Eghf0 <- GH_stof %>% filter(length < 20)
Eapf0 <- AP_stof %>% filter(length < 30)

# table(Eacf0$pa, Eacf0$year)
# table(Eacf1$pa, Eacf1$year)
# table(Eacf2$pa, Eacf2$year)
# table(Eapf0$pa, Eapf0$year)
# table(Eapf1$pa, Eapf1$year)
# table(Eghf0$pa, Eghf0$year)
# table(Eghf1$pa, Eghf1$year)
# table(Eghf2$pa, Eghf2$year)

@@

### Total
```{r}
Eac0 <- rbind(Eacs0, Eacf0) %>% mutate(alt.name = "Atlantic cod")
Eac1 <- rbind(Eacs1, Eacf1) %>% mutate(alt.name = "Atlantic cod")
Eac2 <- rbind(Eacs2, Eacf2) %>% mutate(alt.name = "Atlantic cod")
Eap0 <- rbind(Eaps0, Eapf0) %>% mutate(alt.name = "American plaice")
Eap1 <- rbind(Eaps1, Eapf1) %>% mutate(alt.name = "American plaice")
Egh0 <- rbind(Eghs0, Eghf0) %>% mutate(alt.name = "Greenland halibut")
Egh1 <- rbind(Eghs1, Eghf1) %>% mutate(alt.name = "Greenland halibut")
Egh2 <- rbind(Eghs2, Eghf2) %>% mutate(alt.name = "Greenland halibut")

@@

Cacs1 <- AC_stos %>% filter(length > 17 & length <= 45)
Cacs2 <- AC_stos %>% filter(length > 45)
Cghs1 <- GH_stos %>% filter(length > 19 & length <= 40)
Cghs2 <- GH_stos %>% filter(length > 40)
Caps1 <- AP_stos %>% filter(length > 29)

Cacs0 <- AC_stos %>% filter(length < 18)
Cghs0 <- GH_stos %>% filter(length < 20)
Caps0 <- AP_stos %>% filter(length < 30)

# table(Cacs0$pa, Cacs0$year)
# table(Cacs1$pa, Cacs1$year)
# table(Cacs2$pa, Cacs2$year)
# table(Cghs0$pa, Cghs0$year)
# table(Cghs1$pa, Cghs1$year)
# table(Cghs2$pa, Cghs2$year)
# table(Caps0$pa, Caps0$year)
# table(Caps1$pa, Caps1$year)

@@

# For supplemental
Cacf1 <- AC_stof %>% filter(length > 17 & length <= 45)
Cacf2 <- AC_stof %>% filter(length > 45)
Cghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
Cghf2 <- GH_stof %>% filter(length > 40)
Capf1 <- AP_stof %>% filter(length > 29)

Cacf0 <- AC_stof %>% filter(length < 18)
Cghf0 <- GH_stof %>% filter(length < 20)
Capf0 <- AP_stof %>% filter(length < 30)

# table(Cacf0$pa, Cacf0$year)
# table(Cacf1$pa, Cacf1$year)
# table(Cacf2$pa, Cacf2$year)
# table(Capf0$pa, Capf0$year)
# table(Capf1$pa, Capf1$year)
# table(Cghf0$pa, Cghf0$year)
# table(Cghf1$pa, Cghf1$year)
# table(Cghf2$pa, Cghf2$year)

@@

ac <- data.frame(year = seq(1984,2020,1), 
                 ac0_spring = c(dfac0$ac0_spring[1:9], 0, 0, dfac0$ac0_spring[10:35]), # missing 1993, 1994
                 ac1_spring = c(dfac1$ac1_spring),
                 ac2_spring = c(dfac2$ac2_spring),

                 ac0_fall = c(dfac0$ac0_fall[1:9], 0, 0, dfac0$ac0_fall[10:35]), # missing 1993, 1994
                 ac1_fall = c(dfac1$ac1_fall),
                 ac2_fall = c(dfac2$ac2_fall))
write.csv(ac, file = "./Extra/acseason.csv")

@@

@@

  geom_line( aes(x = time, y = ac1, colour = "ac", linetype = "medium"), linewidth = 1.4) +
  geom_line(aes(x = time, y = ac2, colour = "ac", linetype = "large"), linewidth = 1.4) +

  geom_line(aes(x = time, y = gh1, colour = "gh", linetype = "medium"), linewidth = 1.4) +
  geom_line(aes(x = time, y = gh2, colour = "gh", linetype = "large"), linewidth = 1.4) +

  geom_line(aes(x = time, y = ap1, colour = "ap", linetype = "medium"), linewidth = 1.4) +

  scale_x_continuous(name = "Year", expand = c(0.009,0), limits = c(1983.9,1995.4), breaks = c(seq(1983,1995, 2))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.0,1.7)) +
  scale_color_manual(name = "", values = c(trawl = "brown", ac = "#BC8DA0", gh = "#048BA8", ap = "#AFD5AA"),
                     labels = c(trawl = "Trawl", ac = "Atlantic cod", gh = "Greenland halibut", ap = "American plaice")) +
  scale_linetype_manual(name = "", values = c(medium = "solid", large = "dotdash"),
                        labels = c(medium = "Medium", large = "Large")) +
  ggtitle("Engel\na) 3L Spring") +
  theme_classic() +
  theme(legend.position = "none", 
        axis.title.x = element_blank(),
        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))

@@

  geom_line( aes(x = time, y = ac1, colour = "ac", linetype = "medium"), linewidth = 1.4) +
  geom_line(aes(x = time, y = ac2, colour = "ac", linetype = "large"), linewidth = 1.4) +

  geom_line(aes(x = time, y = gh1, colour = "gh", linetype = "medium"), linewidth = 1.4) +
  geom_line(aes(x = time, y = gh2, colour = "gh", linetype = "large"), linewidth = 1.4) +

  geom_line(aes(x = time, y = ap1, colour = "ap", linetype = "medium"), linewidth = 1.4) +

  scale_x_continuous(name = "Year", expand = c(0.009,0), limits = c(1983.9,1995.4), breaks = c(seq(1983,1995, 2))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0)) +
  scale_color_manual(name = "", values = c(trawl = "brown", ac = "#BC8DA0", gh = "#048BA8", ap = "#AFD5AA"),
                     labels = c(trawl = "Trawl", ac = "Atlantic cod", gh = "Greenland halibut", ap = "American plaice")) +
  scale_linetype_manual(name = "", values = c(medium = "solid", large = "dotdash"),
                        labels = c(medium = "Medium", large = "Large")) +
  ggtitle("c) 2J3KL Fall") + 
  theme_classic() +
  theme(legend.position = "none",
        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))

@@

# plot
sc <- ggplot(data = plotdf) +  
  geom_line(aes(x = time, y = ts, colour = "trawl"), linetype = "dashed", linewidth = 1.4) +

  geom_line(aes(x = time, y = ac1, colour = "ac"), linetype = "solid", linewidth = 1.4) +

  geom_line(aes(x = time, y = gh1, colour = "gh"), linetype = "solid", linewidth = 1.4) +

  geom_line(aes(x = time, y = ap1, colour = "ap"), linetype = "solid", linewidth = 1.4) +

@@

  geom_line( aes(x = time, y = ac1, colour = "ac", linetype = "medium"), linewidth = 1.4) +
  geom_line(aes(x = time, y = ac2, colour = "ac", linetype = "large"), linewidth = 1.4) +

  geom_line(aes(x = time, y = gh1, colour = "gh", linetype = "medium"), linewidth = 1.4) +
  geom_line(aes(x = time, y = gh2, colour = "gh", linetype = "large"), linewidth = 1.4) +

  geom_line(aes(x = time, y = ap1, colour = "ap", linetype = "medium"), linewidth = 1.4) +

  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1994.9,2022), breaks = c(seq(1995, 2022, 5))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.32, 1.6)) +
  scale_color_manual(name = "", values = c(trawl = "brown", ac = "#BC8DA0", gh = "#048BA8", ap = "#AFD5AA"),
                     labels = c(trawl = "Trawl", ac = "Atlantic cod", gh = "Greenland halibut", ap = "American plaice")) +
  scale_linetype_manual(name = "", values = c(medium = "solid", large = "dotdash"),
                        labels = c(medium = "Medium", large = "Large")) +
  ggtitle("d) 2J3KL Fall") + 
  theme_classic() + 
  theme(axis.title.y = element_blank(), legend.text = element_text(size = 16), 
        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))

```
## - Figure 2
```{r, fig.height=10, fig.width=14}

p2 <- ggarrange(se,
          sc,
          fe,
          fc,
          nrow = 2, ncol = 2,
          align = "v", common.legend = TRUE,
          legend = "right", legend.grob = ggpubr::get_legend(fc))

ggsave(filename = "inputdata2.tiff", device = "tiff", plot = p2, path = "./Figures",
       dpi = 300, width = 14, height = 10, units = "in")
